Direction-aware functional class scoring enrichment analysis of Infinium DNA methylation data

### 2024-01-15 manuscript/manuscript.Rmd
example workflow online

Code to generate the results shown here are included in a GitHub repository (https://github.com/markziemann/gmea/).
To enable reproduction of the findings, a docker image is made available at DockerHub
(https://hub.docker.com/repository/docker/mziemann/gmea/general), and an example workflow can be found
in the GitHub repository (https://github.com/markziemann/gmea/tree/main/example_workflow).

>>>>

Code to generate the results shown here are included in a GitHub repository (https://github.com/markziemann/gmea/).
To enable reproduction of the findings, a docker image is made available at DockerHub
(https://hub.docker.com/repository/docker/mziemann/gmea/general).
A reproducible example workflow report is hosted on our website (https://ziemann-lab.net/public/gmea/example_workflow.html).
